The demographics for Cohorts 1 to 7 are summarized in Table \ref{table:cohort_summary}. Cohorts 1 and 2 were sampled from the same set of visit pairs, comprising a 
maximum of 140 subjects with PD state = ``Off" for both visits. Cohort 2 randomly sampled one visit pair for each of the available subjects and 
distributed them to each class as evenly as possible. This resulted in 81 stable subjects and 59 progressive subjects. The mean age and standard deviation for the stable subjects 
is 60.5±9.6 and 62.0±9.4 for the progressive subjects. There are 32 females and 49 males in the stable group, 19 females and 40 males in the progressive group. 
Regarding H\&Y scores, 9 stable subjects have a score of 1, 71 a score of 2, and 1 has a score of 3. For the progressive subjects, 46 have an H\&Y 
score = 1 and 13 have an H\&Y score = 2. Cohort 1 is the smallest of the constructed cohorts with only 31 stable and 31 progressive subjects for a total of 62 
subjects. The stable and progressive groups are composed of 11 females and 20 males, and 12 females and 19 males respectively. The mean age and standard deviation for the stable 
subjects is 60.6±7.2 and 61.4±8.1 for the progressive subjects. There are 18 subjects with H\&Y score = 1 and 13 with score = 2 for both the stable and progressive 
groups.

Cohorts 3 and 4 sampled from a set of visit pairs for 194 subjects with either PD state = ``Off" or PD state =``On" for both visits. Cohort 3 has 102 subjects with 
51 subjects in each class. The stable group has 17 females and 34 males, whereas the progressive group has 19 females and 32 males. The mean age and standard deviation for the stable 
subjects and progressive subjects is 60.3±8.8 and 62.9±8.7 respectively. Both the stable and progressive groups have 25 subjects with H\&Y score = 1 and 26 subjects 
with H\&Y score = 2. Cohort 4 is the largest cohort and is composed of 105 stable subjects and 89 progressive subjects. The mean age and standard deviation for the 
stable and progressive groups are similar to one another at 62.1±9.7 and 62.7±10.0 respectively. Cohort 4 has 41 females and 64 males in the stable group, whereas the 
progressive group has 32 females and 57 males. The number of subjects in the stable group that have H\&Y score = 1 is 11, H\&Y score = 2 is 92, and H\&Y score = 3 is 2. 
The number of subjects in the progressive group that have an H\&Y score of 1, 2, or 3 are 63, 24, and 1 respectively.

Cohorts 5 and 6 sampled from the set of visit pairs defined for the 147 subjects with PD state = ``On" for both visits. Cohort 5 has 74 subjects evenly distributed into stable 
and progressive groups of 37 each. The stable group is composed of 11 females and 26 males, and the progressive group has 14 females and 23 males. The mean age and standard 
deviation for the stable group is 59.0±0.0 and 63.9±9.4 for the progressive group. There are 18 subjects in each group with H\&Y score = 1 and 19 subjects in each group 
with H\&Y score = 2. Cohort 6 has 90 stable subjects and 57 progressive subjects for a total of 147 subjects. The stable group is composed of 36 females and 54 males with a mean 
age and standard deviation of 63.0±9.9, and the progressive group has 21 females and 36 males with a mean age of 62.9±10.1. The stable group has 8 subjects with H\&Y score = 1, 82 subjects 
with H\&Y score = 2, and 0 subjects with H\&Y score = 3. In contrast, the progressive group has 38 subjects with H\&Y score = 1, 18 subjects with H\&Y score = 2, and 1 subjects with 
H\&Y score = 3. 

Cohort 7 is the only cohort that samples from a set of visit pairs for 213 subjects without any restrictions for the PD state of a patient. This cohort was developed as a 
reference cohort for comparison with those created by ~\cite{shu2021predicting} and ~\cite{Arafe2023.05.05.539590}. Cohort 7 has 61 stable and 61 progressive subjects for a total 
of 122 subjects. There are 23 females and 38 males in the stable group and 26 females and 35 males in the progressive group. The mean age and standard deviation is 60.1±9.2 and 
62.3±9.2 for the stable and progressive groups respectively. The stable and progressive groups each have 35 subjects with H\&Y score = 1 and 26 subjects with H\&Y score = 2. 